Gene set analysis misuse examples

### 2021-12-07 examples/examples.Rmd
one command execute

---
title: "Example gene set analysis: bringing it together"
author: "Mark Ziemann & Kaumadi Wijesooriya"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

Previously we analysed five datasets below and looked at the differences between FCS and ORA methods for gene set enrichment.

@@

```{r,begin}

@@

@@

```{r,getdata,fig.width=7,fig.height=5}

@@

```{r,summary_stats}

@@

```{r,jacbox}

@@

```{r,jacbar}

@@

```{r,session}

>>>>

---
title: "Gene set analysis misuse examples"
author: "Mark Ziemann & Kaumadi Wijesooriya"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 7
    fig_height: 5
theme: cosmo
---

@@

This script is designed to generate the results of the manuscript figure 4.

Panels A-D are generated with "example1.Rmd" and "example1-7.Rmd" are required 
for panel E.

Here are the datasets considered.

@@

```{r,begin0}

@@

## Execute the examples

Here I'm running the scripts to analyse each of the example datasets shown in the above
table.

```{r,execute0}

rmarkdown::render("example1.Rmd")
rmarkdown::render("example2.Rmd")
rmarkdown::render("example3.Rmd")
rmarkdown::render("example4.Rmd")
rmarkdown::render("example5.Rmd")
rmarkdown::render("example6.Rmd")
rmarkdown::render("example7.Rmd")

@@

```{r,getdata0,fig.width=7,fig.height=5}

@@

```{r,summary_stats0}

@@

```{r,jacbox0}

@@

```{r,jacbar0}

@@

```{r,session0}
